Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
fixed to 6 pages

\begin{abstract}
%% Text of abstract
Quality assurance (QA) is an important task in manufacturing to assess whether products 
meet their specifications. However, QA might be expensive, time-consuming, incomplete, or delayed.
This paper presents a solution for predictive analytics in QA based on machine sensor values during
production while employing specialized machine-learning models for classification in a controlled environment. 
Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in
further industrial applications. The paper’s outcome proves that the developed model was able to predict
product quality, as well as to identify the correlation between machine-status and faulty product occurrence.
\end{abstract}

\begin{keyword}
Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Logistic Regression

@@

Industrial projects require to work with a variety of sensors and controllers from different manufacturers. Thus, there is a risk of incompatibility between technologies. To avoid that problem, universal protocols are often implemented in industrial projects. This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.

The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell. In our case, the data is acquired independently from two OPC-UA servers. This represents the interaction between multiple servers in real production environments.

@@

Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{goodfellow2016deep}. In our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems were not completely synchronized, as common in practice, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}. The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacturer. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on human-readable words predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

@@

\begin{table}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $8$ & $24$ & $8+24 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+8 = 26$} & \multicolumn{    1}{c}{$0+24 = 24$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Support Vector Machine.}
              \label{tab:SVM_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $6$ & $26$ & $6+26 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+6 = 24$} & \multicolumn{    1}{c}{$0+26 = 26$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Multilayer Perceptron.}
              \label{tab:MPL_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $17$ & $1$ & $17+1 = 18$\\
                     \cline{2-4}
                     & NOK & $0$ & $32$ & $0+32 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$17+0 = 17$} & \multicolumn{    1}{c}{$1+32 = 33$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Decision Tree.}
              \label{tab:Tree_conf_matrix}
       \end{subtable}
       \caption{Confusion matrices result of the prediction of 50 test data-points. We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions. The tables read from the upper-left cell to the right-cell as: true-positive, false-positive, false-negative, true-negative.}
       \label{tab:Confusion_matrix}
\end{table}

>>>>

\begin{abstract}
%% Text of abstract
Quality assurance (QA) is an important task in manufacturing to assess whether products 
meet their specifications. However, QA might be expensive, time-consuming, or incomplete.
This paper presents a solution for predictive analytics in QA based on machine sensor values during
production while employing specialized machine-learning models for classification in a controlled environment. 
Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in
further industrial applications. The paper’s outcome proves that the developed model was able to predict
product quality, as well as to identify the correlation between machine-status and faulty product occurrence.
\end{abstract}

\begin{keyword}
Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Classification

@@

Industrial projects require to work with a variety of sensors and controllers from different manufacturers. Thus, the risk of incompatibility between technologies increases. To avoid these problems, universal protocols are often implemented in industrial projects. Figure~\ref{fig:demo_conn_diag} describes a simplified version of the real connection diagram of the demonstration cell. In our case, the data is acquired independently from two OPC-UA servers. This represents the interaction between multiple servers in real production environments.

@@

Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{bishop2006pattern}. In our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems were not completely synchronized, as common in practice, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process \cite{bishop2006pattern}. The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacturer. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on human-readable words predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

@@

\begin{table}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $8$ & $24$ & $8+24 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+8 = 26$} & \multicolumn{    1}{c}{$0+24 = 24$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Support Vector Machine.}
              \label{tab:SVM_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $6$ & $26$ & $6+26 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+6 = 24$} & \multicolumn{    1}{c}{$0+26 = 26$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Multilayer Perceptron.}
              \label{tab:MPL_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $17$ & $1$ & $17+1 = 18$\\
                     \cline{2-4}
                     & NOK & $0$ & $32$ & $0+32 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$17+0 = 17$} & \multicolumn{    1}{c}{$1+32 = 33$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Decision Tree.}
              \label{tab:Tree_conf_matrix}
       \end{subtable}
       \caption{Confusion matrices result of the prediction of 50 test data-points. We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions. The tables read from the upper-left cell as: true-positive, false-positive, false-negative, true-negative.}
       \label{tab:Confusion_matrix}
\end{table}
